Model Estimation

### 2018-12-07 model_estimation.Rmd
Fix bug where park/tract distance matrix was built inverted

#' Calculate destination choice logsums from a distance matrix
#' 
#' @param distances An $n\times p$ matrix with the distance from all tracts to
#'   all parks in miles.
#' @param sizes A p-length vector of park sizes
#' @param tweets A p-length vector of tweets at parks
#' @param betas A vector containing the size, distance, and tweet coefficients. 
#'   If we submit two variables the tweets are ignored.
#'   
#' @return An n-length vector containing the weighted log-sum based
#'   accessibility between a tract and all parks.
#' @details If we have n tracts and p parks, distances needs to be a 
#' 
calculate_park_logsums <- function(distances, sizes, tweets = NULL,
                                   betas = c(-15,.00001, .001)){

  # A is n x p
  a <- betas[1] * distances

@@

# distances from all tracts to all zones
distances <- st_distance(park_centroids, tract_centroids, byid = TRUE) %>%
  units::set_units(miles) %>%
  units::drop_units()
```

@@

  estimation_data <- tracts@data %>% 
    mutate(logsum = calculate_park_logsums(
      distances,  parks$log_size,
      betas = betas))

@@

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 0), # distance, size 
  lower = c(-100, -100), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  hessian=TRUE, distances = log(distances[1:10, 1:10]), parks = parks[1:10,], tracts = tracts[1:10, ], 
  model = obese_base_lm, method = "L-BFGS-B", control = list(trace = 6))
```

>>>>

#' Calculate destination choice logsums from a distance matrix
#' 
#' @param d An $n\times p$ matrix with the distance from all tracts to
#'   all parks
#' @param sizes A p-length vector of park sizes
#' @param tweets A p-length vector of tweets at parks
#' @param betas A vector containing the size, distance, and tweet coefficients. 
#'   If we submit two variables the tweets are ignored.
#'   
#' @return An n-length vector containing the weighted log-sum based
#'   accessibility between a tract and all parks.
#' @details If we have n tracts and p parks, distances needs to be a 
#' 
calculate_park_logsums <- function(d, sizes, tweets = NULL,
                                   betas = c(-15,.00001, .001)){

  # A is n x p
  a <- betas[1] * d

@@

# distances from all tracts to all zones
distances <- st_distance(tract_centroids, park_centroids, byid = TRUE) %>%
  units::set_units(miles) %>%
  units::drop_units()
```

@@

  estimation_data <- tracts@data %>% 
    mutate(logsum = calculate_park_logsums(
      d = distances,  parks$log_size,
      betas = betas))

@@

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 0), # distance, size 
  lower = c(-100, -100), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  hessian=TRUE, distances = log(distances), parks = parks, tracts = tracts, 
  model = obese_base_lm, method = "L-BFGS-B", control = list(trace = 6))
```
